```{r}
library(randomForest)
library(caret)
library(e1071)
library(rpart)
library(rpart.plot)

```

Building the model by using Decision tree

```{r}
# Decision Tree using 5 attrbutes and 1000 training tuples and 10000 testing tuples

decision_tree_model <- rpart(result ~ protocol_type+srv_rerror_rate+flag+rerror_rate+logged_in, data = training2[1:1000,], method = "class")

# Predicting:
decision_tree_pred <- predict(decision_tree_model, testing_data[1:10000,], type = "class")
decision_tree_pred

testing_data=training2[100000:125973,]
right <- decision_tree_pred==testing_data[1:10000,"result"]
answer<-table(decision_tree_pred,testing_data[1:10000,"result"])
answer
round(prop.table(answer,1)*100,2)

# Plot of the Decision Tree
rpart.plot(decision_tree_model, main = "Classification Tree", 
           extra = 102, under = TRUE, faclen = 0)

# Test results on our subTesting data set:
confusionMatrix(prediction1, subTesting$classe)
```

                  
decision_tree_pred  dos normal probe  r2l  u2r
            dos    3310    242    91    5    0
            normal  145   4936   130   76    3
            probe   238    125   698    1    0
            r2l       0      0     0    0    0
            u2r       0      0     0    0    0
> round(prop.table(answer,1)*100,2)
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos    90.73   6.63  2.49  0.14  0.00
            normal  2.74  93.31  2.46  1.44  0.06
            probe  22.41  11.77 65.73  0.09  0.00
            r2l                                  
            u2r            

```{r}
# Decision Tree using 5 attrbutes and 100000 training tuples and 25974 testing 

decision_tree_model <- rpart(result ~ protocol_type+srv_rerror_rate+flag+rerror_rate+logged_in, data = training2[1:100000,], method = "class")


# Predicting:
decision_tree_pred <- predict(decision_tree_model, testing_data[1:25974,], type = "class")
decision_tree_pred


right <- decision_tree_pred==testing_data[1:25974,"result"]
answer<-table(decision_tree_pred,testing_data[1:25974,"result"])
answer
round(prop.table(answer,1)*100,2)

# Plot of the Decision Tree
rpart.plot(decision_tree_model, main = "Classification Tree", 
           extra = 102, under = TRUE, faclen = 0)

# Test results on our subTesting data set:
confusionMatrix(prediction1, subTesting$classe)
```            
> answer
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos     8484    636   200    14     0
            normal   364  12925   357   190     9
            probe    619    337  1836     3     0
            r2l        0      0     0     0     0
            u2r        0      0     0     0     0
> round(prop.table(answer,1)*100,2)
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos    90.89   6.81  2.14  0.15  0.00
            normal  2.63  93.36  2.58  1.37  0.07
            probe  22.15  12.06 65.69  0.11  0.00
            r2l                                  
            u2r 
            


```{r}
# Decision Tree using 8 attrbutes and 1000 training tuples and 25974 testing 


decision_tree_model <- rpart(result ~ protocol_type+srv_rerror_rate+flag+rerror_rate+logged_in+dst_host_rerror_rate+src_bytes+ serror_rate+rerror_rate, data = training2[1:100000,], method = "class")


# Predicting:
decision_tree_pred <- predict(decision_tree_model, testing_data[1:25974,], type = "class")
decision_tree_pred


right <- decision_tree_pred==testing_data[1:25974,"result"]
answer<-table(decision_tree_pred,testing_data[1:25974,"result"])
answer
round(prop.table(answer,1)*100,2)

# Plot of the Decision Tree
rpart.plot(decision_tree_model, main = "Classification Tree", 
           extra = 102, under = TRUE, faclen = 0)

# Test results on our subTesting data set:
confusionMatrix(prediction1, subTesting$classe)
```       

round(prop.table(answer,1)*100,2)
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos    93.69   5.44  0.87  0.00  0.00
            normal  1.47  96.55  0.43  1.50  0.05
            probe   0.00  16.49 83.17  0.26  0.07
            r2l                                  
            u2r       
         

```{r}
# Decision Tree using 8 attrbutes and 10000 training tuples and 25974 testing 


decision_tree_model <- rpart(result ~ protocol_type+srv_rerror_rate+flag+rerror_rate+logged_in+dst_host_rerror_rate+src_bytes+ serror_rate+rerror_rate, data = training2[1:100000,], method = "class")


# Predicting:
decision_tree_pred <- predict(decision_tree_model, test.final, type = "class")
decision_tree_pred


right <- decision_tree_pred==test.final[,"result"]
answer<-table(decision_tree_pred,test.final[,"result"])
answer
round(prop.table(answer,1)*100,2)

# Plot of the Decision Tree
rpart.plot(decision_tree_model, main = "Classification Tree", 
           extra = 102, under = TRUE, faclen = 0)

# Test results on our subTesting data set:
confusionMatrix(prediction1, subTesting$classe)
```
answer
                  
decision_tree_pred  dos normal probe  r2l  u2r
            dos    5151     82   108  187    0
            normal  359   9226     1 1570   35
            probe   231    402   997  442    2
            r2l       0      0     0    0    0
            u2r       0      0     0    0    0
            `             
 round(prop.table(answer,1)*100,2)
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos    93.18   1.48  1.95  3.38  0.00
            normal  3.21  82.44  0.01 14.03  0.31
            probe  11.14  19.38 48.07 21.31  0.10
            r2l                                  
            u2r
            
            

```{r}
# Decision Tree using 5 attrbutes and 100000 training tuples and 25974 testing 

decision_tree_model <- rpart(result ~ protocol_type+srv_rerror_rate+flag+rerror_rate+logged_in, data = training2[1:100000,], method = "class")


# Predicting:
decision_tree_pred <- predict(decision_tree_model, testing_data[1:25974,], type = "class")
decision_tree_pred


right <- decision_tree_pred==testing_data[1:25974,"result"]
answer<-table(decision_tree_pred,testing_data[1:25974,"result"])
answer
round(prop.table(answer,1)*100,2)

# Plot of the Decision Tree
rpart.plot(decision_tree_model, main = "Classification Tree", 
           extra = 102, under = TRUE, faclen = 0)

# Test results on our subTesting data set:
confusionMatrix(prediction1, subTesting$classe)
```            
> answer
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos     8484    636   200    14     0
            normal   364  12925   357   190     9
            probe    619    337  1836     3     0
            r2l        0      0     0     0     0
            u2r        0      0     0     0     0
> round(prop.table(answer,1)*100,2)
                  
decision_tree_pred   dos normal probe   r2l   u2r
            dos    90.89   6.81  2.14  0.15  0.00
            normal  2.63  93.36  2.58  1.37  0.07
            probe  22.15  12.06 65.69  0.11  0.00
            r2l                                  
            u2r 
            
