

## Building the model using random forest classifier

```{r}
library(randomForest)
library(caret)
library(e1071)


```
## creating one more temporary table called kddcopy modifying result column of that to labels
#number of attributes: 6 training data size: 1262 , testing data size: 124711

```{r}
data1<-kddcopy[,c("srv_rerror_rate",   "rerror_rate", "flag",  "dst_host_rerror_rate", "logged_in", "protocol_type","result" )] 


inTrain <- createDataPartition(y=data1$result,p=0.01, list=FALSE)
training <- data1[inTrain,]
testing <- data1[-inTrain,]
dim(training)



modFit <- train(result ~ .,method="rf",data=training)
modFit


pred <- predict(modFit,testing) 
testing$predRight <- pred==testing$result
answer<-table(pred,testing$result)
round(prop.table(answer,1)*100,2)

```
 Output:
>answer
        


pred       dos normal probe   r2l   u2r
  dos    41277   2377   576     0     0
  normal  1231  62162  1209   928    51
  probe   2959   2130  9754    57     0
  r2l        0      0     0     0     0
  u2r        0      0     0     0     0
> round(prop.table(answer,1)*100,2)
        
pred       dos normal probe   r2l   u2r
  dos    93.32   5.37  1.30  0.00  0.00
  normal  1.88  94.79  1.84  1.42  0.08
  probe  19.86  14.30 65.46  0.38  0.00
  r2l                                  
  u2r 

#number of attributes: 5 training data size: 1262 , testing data size: 124711


```{r}

data1<-kddcopy[,c("srv_rerror_rate",   "rerror_rate", "flag",  "dst_host_rerror_rate", "logged_in","result" )] 


inTrain <- createDataPartition(y=data1$result,p=0.01, list=FALSE)
training <- data1[inTrain,]
testing <- data1[-inTrain,]
dim(training)



modFit <- train(result ~ .,method="rf",data=training)
modFit


pred <- predict(modFit,testing) 
testing$predRight <- pred==testing$result
answer<-table(pred,testing$result)
round(prop.table(answer,1)*100,2)

```
        
pred       dos normal probe   r2l   u2r
  dos    93.04   5.41  1.55  0.00  0.00
  normal  5.44  86.20  7.03  1.26  0.07
  probe   3.05  10.85 85.29  0.81  0.00
  r2l                                  
  u2r


#readin test data
#number of attributes: 6 training data size: 12600 , testing data size: 113373
```{r}
data1<-kddcopy[,c("srv_rerror_rate",   "rerror_rate", "flag",  "dst_host_rerror_rate", "logged_in","result" )] 


inTrain <- createDataPartition(y=data1$result,p=0.1, list=FALSE)
training <- data1[inTrain,]
testing <- data1[-inTrain,]
dim(training)



modFit <- train(result ~ .,method="rf",data=training)
modFit


pred <- predict(modFit,testing) 
testing$predRight <- pred==testing$result
answer<-table(pred,testing$result)
round(prop.table(answer,1)*100,2)

```

pred       dos normal probe   r2l   u2r
  dos    94.32   5.23  0.45  0.00  0.00
  normal  5.23  86.31  7.13  1.26  0.07
  probe   6.91   7.76 85.13  0.19  0.02
  r2l     0.00   0.00 23.40 76.60  0.00
  



#number of attributes: 6 training data size: 25197 , testing data size: 100776


```{r}
data1<-kddcopy[,c("srv_rerror_rate",   "rerror_rate", "flag",  "dst_host_rerror_rate", "logged_in","result" )] 


inTrain <- createDataPartition(y=data1$result,p=0.2, list=FALSE)
training <- data1[inTrain,]
testing <- data1[-inTrain,]
dim(training)



modFit <- train(result ~ .,method="rf",data=training)
modFit


pred <- predict(modFit,testing) 
testing$predRight <- pred==testing$result
answer<-table(pred,testing$result)
round(prop.table(answer,1)*100,8)

```
TIme taken:  11:50 to 12:18
pred       dos normal probe   r2l   u2r
  dos    94.31   5.25  0.44  0.00  0.00
  normal  5.13  86.36  7.17  1.26  0.07
  probe   7.18   6.18 86.55  0.09  0.00
  r2l     0.00   3.64 32.73 63.64  0.00
  u2r  
  

#number of attributes: 9 training data size: 12600 , testing data size: 113373
  
```{r}
data1<-kddcopy[,c("srv_rerror_rate",  "protocol_type" ,"src_bytes", "rerror_rate", "flag",  "dst_host_rerror_rate", "logged_in","result","service"  ,"serror_rate"    )] 


inTrain <- createDataPartition(y=data1$result,p=0.1, list=FALSE)
training <- data1[inTrain,]
testing <- data1[-inTrain,]
dim(training)



modFit <- train(result ~ .,method="rf",data=training)
modFit


pred <- predict(modFit,testing) 
testing$predRight <- pred==testing$result
answer<-table(pred,testing$result)
round(prop.table(answer,1)*100,2)

```
pred       dos normal probe   r2l   u2r
  dos    98.92   0.53  0.55  0.00  0.00
  normal  0.36  98.86  0.23  0.47  0.07
  probe   0.00   2.37 97.54  0.07  0.02
  r2l     0.00   6.86  0.00 93.14  0.00
  u2r

#number of attributes: 9 training data size: 12625 , testing data size: 124711 and test data as test.final 


```{r}
data1<-kddcopy[,c("srv_rerror_rate",  "protocol_type" ,"src_bytes", "rerror_rate", "flag",  "dst_host_rerror_rate", "logged_in","result","service"  ,"serror_rate"    )] 


inTrain <- createDataPartition(y=data1$result,p=0.1, list=FALSE)
training <- data1[inTrain,]
testing <- data1[-inTrain,]
dim(training)



modFit <- train(result ~ .,method="rf",data=training)
modFit


pred <- predict(modFit,test.final) 
testing$predRight <- pred==test.final$result
answer<-table(pred,test.final$result)
round(prop.table(answer,1)*100,2)

```

1262 samples
   9 predictor
   5 classes: 'dos', 'normal', 'probe', 'r2l', 'u2r' 

No pre-processing
Resampling: Bootstrapped (25 reps) 
Summary of sample sizes: 1262, 1262, 1262, 1262, 1262, 1262, ... 
Resampling results across tuning parameters:

  mtry  Accuracy   Kappa    
   2    0.8523705  0.7218909
  44    0.9785942  0.9623108
  87    0.9752067  0.9568197

Accuracy was used to select the optimal model using  the largest value.
The final value used for the model was mtry = 44. 

> round(prop.table(answer,1)*100,2)
        
pred       dos normal probe   r2l   u2r
  dos    96.82   1.68  1.50  0.00  0.00
  normal  0.75  80.21  0.23 18.50  0.31
  probe  23.09  12.35 64.49  0.06  0.00
  r2l     0.00  10.71  0.00 89.29  0.00
  u2r 
  